### 2020-01-18 nlp_models.tex
still need to fix snorm plots
updated NLP plots

In the past two years, nearly 100 open source, pre-trained DNNs for Natural Language Processing (NLP) have emerged,
based on the revolutionary Transformer architecture, including variants of BERT, Transformer-XML, GPT, etc.
The Transformer architectures consist of blocks of Attention layers, containing of 2 large, Feed Forward (Linear)
weight matrics \cite{Attn2017}. In contrast to the smaller pre-Activation maps arising in Cond2D layers,
the Attention matrices ar

\paragraph{GPT vs GPT2}
Here, we use the \emph{WeightWatcher} tool to analyze the OpenAI GPT and GPT2 models, which gives us
the opportunity to analyze the effect of both training the same model with different size data sets,
These GPT models have generated significant media attention because of its remarkable ability to
 generate fake text, and it's potential misuse. 
The original GPT and later GPT model have the same architecture and number of layers, but
the original GPT was released having been trained on a deficient data set.  Recently,
 however, a much improved GPT2 model has been released, which is remarkably good at creating 
auto-genetated text.

@@

\begin{figure}
   \includegraphics[scale=0.25]{img/GPT-alpha-hist.png}
   \caption{Comparison of heavy tailed power law exponent $\alpha$ for OpenAI GPT and GPT pretrained models}
   \label{fig:gpt-alpha-hist.png}
\end{figure}

@@

    \subfigure[ Power Law Exponent $\alpha$  ]{
        \includegraphics[width=4.5cm]{img/GPT2_all_alpha_hist.png}
        \label{fig:gpt-alpha-layer}
    }
    \qquad
    \subfigure[ Spectral Norm $\Vert\mathbf{W}\Vert_{\infty}$]{
        \includegraphics[width=4.5cm]{img/GPT2_all_spectralnorm_hist.png}
        \label{fig:resnet-snorm-layer}
    }
    \qquad
    \subfigure[ Alpha-Norm $\Vert\mathbf{X}\Vert_{\alpha}^{\alpha}$]{
        \includegraphics[width=4.5cm]{img/GPT2_all_alpha_weighted_hist.png}
        \label{fig:gpt-pnorm-layer}
    }
    \caption{Comparison of Power Law Exponnents, Spectral Norm, and Alpha-Norm for different size models in the GPT2 architecture series.  Spectral Norm dhistogram does not contain the first 2 layers because the values are unusually large. }
    \label{fig:gpt-alpha-layers}
\end{figure}

>>>>

In the past two years, nearly 100 open source, pre-trained DNNs for Natural Language Processing (NLP) have emerged,
based on the revolutionary Transformer architecture, including variants of BERT, Transformer-XML, GPT, etc.
The Transformer architectures consist of blocks of Attention layers, containing of 2 large, Feed Forward (Linear)
weight matrics \cite{Attn2017}. In contrast to the smaller pre-Activation maps arising in Cond2D layers,
the Attention matrices are significantly larger, and frequently under-correlated, with generally larger
Heavy Tailed Power Law exponents $\alpha$ (when fitting the ESD).

\paragraph{OpenAI GPT Models}
Here, we use the \emph{WeightWatcher} tool to analyze the OpenAI GPT and GPT2 models, which gives us
the opportunity to analyze the effect of both training the same model with different size data sets,
and increasing sizes of both the data set and architectures.
These models have generated significant media attention because of their remarkable ability to
 generate fake text that appears to be real and the potential misuse of this.
For this reason, the original GPT model was trained on on a deficient data set, rendering
the model interesting but not fully functional.  Later, the same GPT model 
The original GPT and later GPT model have the same architecture and number of layers, but

 however, a much improved GPT2 model has been released, which is remarkably good at creating 
auto-genetated text.

@@

\begin{figure}
    \centering
    \subfigure[Power Law Exponent $\alpha$]{
        \includegraphics[width=5cm]{img/GPT-alpha-hist.png}
        \label{fig:GPT-alpha.hist.png}
       }
    \qquad
    \subfigure[Log Spectral Norm $\log\Vert\mathbf{W}\Vert_{\infty}$]{
        \includegraphics[width=5cm]{img/GPT-snorm-hist.png}
        \label{fig:GPT-snorm.hist.png}
       }

   \caption{Comparison of Heavy Tailed Power Law exponents $\alpha$, and log Spectral Norms $\log\Vert\mathbf{W}\Vert_{\infty}$
for the OpenAI GPT and GPT2 (small) pretrained models.}

\end{figure}

@@

    \subfigure[ Power Law Exponent $\alpha$  ]{
        \includegraphics[width=4.5cm]{img/GPT2_all_alpha_hist.png}
        \label{fig:gpt-alpha-layer}
    }
    \qquad
    \subfigure[ Spectral Norm $\Vert\mathbf{W}\Vert_{\infty}$]{
        \includegraphics[width=4.5cm]{img/GPT2_all_spectralnorm_hist.png}
        \label{fig:resnet-snorm-layer}
    }
    \qquad
    \subfigure[ Alpha-Norm $\Vert\mathbf{X}\Vert_{\alpha}^{\alpha}$]{
        \includegraphics[width=4.5cm]{img/GPT2_all_alpha_weighted_hist.png}
        \label{fig:gpt-pnorm-layer}
    }
    \caption{Comparison of Power Law Exponnents, Spectral Norm, and Alpha-Norm for different size models in the GPT2 architecture series.  Spectral Norm dhistogram does not contain the first 2 layers because the values are unusually large.}
    \label{fig:gpt-alpha-layers}
\end{figure}
